\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-02-12 paper.qmd
Added new spin-brush trials

library(grid)
# library(xtable)
# 
# xtable2kable <- function(x) {
#   out <- capture.output(print(x, table.placement = NULL))[-(1:2)]
#   out <- paste(out, collapse = "\n")
#   structure(out, format = "latex", class = "knitr_kable")
# }

@@

@@

@@

@@

@@

>>>>

library(grid)

# ## For paralleization
# library(foreach)
# library(doParallel)

# library(xtable)
# 
# xtable2kable <- function(x) {
#   out <- capture.output(print(x, table.placement = NULL))[-(1:2)]
#   out <- paste(out, collapse = "\n")
#   structure(out, format = "latex", class = "knitr_kable")
# }

@@

The following steps will help to find a suitable value to remove low density hexagons:

1. Plot the distribution of the standardized counts

2. See the distribution of counts

3. Take the first quartile

@@

cell_count_plot_s_curve <- ggplot(df_bin_centroids_umap_s_curve, aes(x = reorder(as.factor(hexID), -std_counts), y = std_counts)) +
  geom_quasirandom() + xlab("hexagonal id") + ylab("Standardized cell count") +
  geom_hline(yintercept = 0.20, colour = "#de2d26") +
  theme(axis.text = element_text(size = 5),
        axis.title = element_text(size = 7),
        axis.text.x = element_text(angle = 90))

@@

The following steps will help to find a suitable value to remove long edges:

1. Plot the distribution of the 2D distances

2. Find a value which is greater than smallest value

@@

distance_plot_s_curve <- plot_dist(distance_umap_s_curve) +
  #ggtitle("(b)" ) +
  ylab(expression(d^{(2)})) +
  theme(axis.text = element_text(size = 5),
        axis.title = element_text(size = 12))

@@

```{r}
#| warning: false
#| echo: false
#| label: fig-modelScurverdistcount
#| fig-cap: "plots to identify benchmark values"
##| out-width: 100%
#| fig-pos: H

cell_count_plot_s_curve + distance_plot_s_curve +
  #plot_annotation(tag_levels = 'a') +
  plot_layout(ncol = 2) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```

### 2024-02-12 paper.tex
Added new spin-brush trials

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

@@

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-55-1.pdf}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, breakable, interior hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

The following steps will help to find a suitable value to remove low
density hexagons:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Plot the distribution of the standardized counts
\item
  See the distribution of counts
\item
  Take the first quartile
\end{enumerate}

@@

The following steps will help to find a suitable value to remove long
edges:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Plot the distribution of the 2D distances
\item
  Find a value which is greater than smallest value
\end{enumerate}

{\centering \includegraphics{paper_files/figure-pdf/fig-modelScurverdistcount-1.pdf}

\caption{\label{fig-modelScurverdistcount}plots to identify benchmark
values}

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-56-1.pdf}
